---
title: "Assignment6"
author: "Jiner Zheng"
date: "4/5/2018"
output: html_document
---

```{r, warning=FALSE, message=FALSE}
require(ggplot2)
require(shiny)
require(maps)
require(mosaic)
require(reshape2)
require(riverplot)
require(RColorBrewer)
Obese2 <- read.csv("/Volumes/courses/QAC/qac251/course_materials/Code and Data/Obese2.csv")
```

a.With the obesity rates data, construct a plot that is similar to the one in DataPoints (Chapter 3, p.128) from earlier in the semester. (Try to get some of the state labels neatly into your graph – notice that it will be difficult to get all labels legible with the amount of space we have available.)
```{r}
names(Obese2)[2]<-c("region")
Obese2<-mutate(Obese2, Year2016=as.numeric(gsub(pattern ="%","",Year2016)),Year1990=as.numeric(gsub(pattern = "%","",Year1990)))
ggplot(data=Obese2)+
  geom_segment(aes(x=as.factor(1990),xend=as.factor(2016),y=Year1990,yend=Year2016,color=region),na.rm=TRUE)+
  geom_point(aes(x=as.factor(2016),y=Year2016,color=region),na.rm = TRUE)+
  geom_point(aes(x=as.factor(1990),y=Year1990,color=region),na.rm = TRUE)+
  theme(legend.position = "none")+
  geom_text(aes(x=as.factor(1990),y=Year1990,color=region,label=region),check_overlap = TRUE,na.rm=TRUE,nudge_x = -0.25,size=2)+
  geom_text(aes(x=as.factor(2016),y=Year2016,color=region,label=region),check_overlap = TRUE,na.rm=TRUE,nudge_x = 0.25,size=2)+
  ylab("Rate")+
  xlab("Year")+
  ggtitle("Obesity Rates Overtime in States")

```

b. Using your plot from part a, list 4 different insights about the data you are able to answer.
1) The Obesity rate has increased significantly from 1990 to 2016.
2) Colorado had the lowest obesity rate in both 1990 and 2016.
3) The obesity rate of West Virginia has increased more than the obesity rate of Mississippi from 1990 to 2016.
4) The obesity rates of all states were a lot lower than 20% in 1990.

C.Make a choropleth to compare how the rates have changed over time. Do you prefer this plot to the one you made in part a? Why?
I prefer the one in Part a, because I can see how much the obesity rates have changed more clearly over time and which states had the highest or lowest obesity rates.
```{r}
all_states<-map_data("state")
Obese2=select(Obese2, "region","Year2016","Year1990")
Obese2=mutate(Obese2, region=tolower(region))
Obese2.long<-melt(Obese2, id="region")
names(Obese2.long)<-c("region","year","rate")
Obese2.long<-mutate(Obese2.long, year=as.numeric(gsub(pattern ="Year","",year),rate=as.numeric(rate)))

ggplot()+
  geom_map(data=all_states, aes(map_id=region), map=all_states)+
  geom_map(data=Obese2.long, aes(map_id=region, fill=rate),map=all_states)+
  expand_limits(x=all_states$long,y=all_states$lat)+
  scale_fill_gradient(low="pink",high="purple")+
  facet_grid(~year)
```

d.Build a shiny app that allows the user to select the states that they would like to investigate from your plot in part a. (For this part, please use the eval=FALSE option in your corresponding code chunk. That is, I just want to see your code.)

```{r}
ui<-fluidPage(
  selectInput(inputId = "myState",
            label="Select a state",
            choices=unique(Obese2$region),
            selected = "west virginia"),
  plotOutput(outputId = "plotspace")
)

server<-function(input,output){
  output$plotspace<-renderPlot({
    ggplot(data=filter(Obese2, region%in%input$myState))+
    geom_segment(aes(x=as.factor(1990),xend=as.factor(2016),y=Year1990,yend=Year2016,color=region),na.rm=TRUE)+
    geom_point(aes(x=as.factor(2016),y=Year2016,color=region),na.rm = TRUE)+
    geom_point(aes(x=as.factor(1990),y=Year1990,color=region),na.rm = TRUE)+
    geom_text(aes(x=as.factor(1990),y=Year1990,color=region,label=region),check_overlap = TRUE,na.rm=TRUE,nudge_x = -0.1)+
    geom_text(aes(x=as.factor(2016),y=Year2016,color=region,label=region),check_overlap = TRUE,na.rm=TRUE,nudge_x = 0.1)+
    ylab("Rate")+
    xlab("Year")+
    ggtitle("Obesity Rates Overtime in States")
  })
}

shinyApp(ui=ui,server=server)
```



PROBLEM2

```{r}
nodes1<-data.frame(ID=c("Packaged Medicaments","Vehicle Parts1","Planes, Helicopters, and/or Spacecraft","Cars1","Refined petroleum1","Exports v.s. Imports","Vehicle Parts2","Refined Petroleum2","Computers","Cars2","Crude Petroleum"),
                  x=c(rep(0,5),5,rep(10,5)),
                  y=c(1:5,3,1:5),
                  col=c(brewer.pal(5,"Accent"),"#000000",brewer.pal(5,"Accent")),
                  labels=c("Packaged Medicaments","Vehicle Parts","Planes, Helicopters, and/or Spacecraft","Cars","Refinedetroleum","Exports v.s. Imports","Vehicle Parts","Refined Petroleum","Computers","Cars","Crude Petroleum"))
nodes1$col<-paste(nodes1$col,95,sep="")
edges1<-data.frame(N1=c("Packaged Medicaments","Vehicle Parts1","Planes, Helicopters, and/or Spacecraft","Cars1","Refined petroleum1",rep("Exports v.s. Imports",5)),
                  N2=c(rep("Exports v.s. Imports",5),"Vehicle Parts2","Refined Petroleum2","Computers","Cars2","Crude Petroleum"),
                  Value=c(38.1,38.4,53.2,60.8,103,62.8,69.2,92,155,230))

river_data1<-makeRiver(nodes1,edges1)

riverplot(river_data1,lty=0,srt=0,default_style = NULL,gravity = "top",node_margin = 1,nodewidth = 1,plot_area = 0.5,nsteps = 50,add_mid_points = NULL,yscale = "auto",text="R")
```

```{r}
nodes2<-data.frame(ID=c("Germany1","Japan1","China1","Mexico1","Canada1","Exports v.s. Imports","Germany2","Japan2","Mexico2","Canada2","China2"),
                  x=c(rep(0,5),1,rep(2,5)),
                  y=c(1:5,3,1:5),
                  col=c(brewer.pal(5,"Accent"),"#000000",brewer.pal(5,"Accent")),
                  labels=c("Germany","Japan","China","Mexico","Canada","Exports v.s. Imports","Germany","Japan","Mexico","Canada","China"))
nodes2$col<-paste(nodes2$col,95,sep="")
edges2<-data.frame(N1=c("Germany1","Japan1","China1","Mexico1","Canada1",rep("Exports v.s. Imports",5)),
                  N2=c(rep("Exports v.s. Imports",5),"Germany2","Japan2","Mexico2","Canada2","China2"),
                  Value=c(61.6,67.5,134,194,241,121,128,291,331,432))

river_data2<-makeRiver(nodes2,edges2)

riverplot(river_data2,lty=0,srt=0,default_style = NULL,gravity = "top",node_margin = 1,nodewidth = 1,plot_area = 0.5,nsteps = 50,add_mid_points = NULL,yscale = "auto",text="R")
```

